Demonstration of matching route networks

### 2024-01-30 r/data-raw/test-large-edinburgh.qmd
Minor update

```{r}
os_joined = stplanr::rnet_merge(
  open_roads |> dplyr::transmute(n = seq(nrow(open_roads))) |> sf::st_transform("EPSG:27700"),
  osm_roads |> sf::st_cast("LINESTRING") |> sf::st_zm() |> sf::st_transform("EPSG:27700"),
  funs = funs,
  dist = 20,
  segment_length = 10
  )
os_joined |>
  dplyr::select(value) |>
  plot(logz = TRUE)
```

>>>>

```{r}
os_joined = stplanr::rnet_merge(
  open_roads |> dplyr::transmute(n = seq(nrow(open_roads))) |> sf::st_transform("EPSG:27700"),
  osm_roads |> sf::st_cast("LINESTRING") |> sf::st_zm() |> sf::st_transform("EPSG:27700"),
  funs = funs,
  dist = 20,
  segment_length = 10
  )
plot(osm_roads$geometry, col = "grey", lwd = 3)
os_joined |>
  sf::st_transform("EPSG:4326") |>
  dplyr::select(value) |>
  plot(logz = TRUE, add = TRUE)

```
